---
title: "Cest2.1_OctAvoidance"
author: "TB"
Date: "2021-2023"
output: 
  html_document:
    code_folding: hide
---

30pct Octanol Avoidance

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
library(ggtext)
theme_set(theme_classic())
files <- fs::dir_ls(recurse = TRUE, glob = "data/octanol_3*.csv")
merged_data <- files %>% purrr::map_df(., readr::read_csv, .id = "filename")
library(dplyr)

```

Plotting by Genotype
```{R}
merged_data %>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in cest-2.1") +
  scale_fill_manual(values = c("green", "grey", "blue", "red", "purple", "orange", "black")) +
  scale_color_manual(values = c("green", "grey", "blue", "red", "purple", "orange", "black"))
  
```
Plot by Date

```{r}
merged_data %>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in cest-2.1") +
  scale_fill_manual(values = c("green", "grey", "blue", "red", "purple","orange", "black")) +
  scale_color_manual(values = c("green", "grey", "blue", "red", "purple", "orange", "black")) +
  facet_grid(~Genotype)
```

Plotting by Genotype (excluding 8-27)
```{R}
merged_data %>%
  filter(Date != "2021-08-27") %>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in cest-2.1") +
  scale_fill_manual(values = c("green", "grey", "blue", "red","purple", "orange", "black")) +
  scale_color_manual(values = c("green", "grey", "blue", "red", "purple", "orange", "black"))
  
```

Plotting by Experimenter

```{r}
merged_data %>%
  filter(Date != "2021-08-27") %>%
  ggplot(aes(x = Experimenter, y = Response.time)) +
  geom_boxplot(aes(fill = Genotype)) +
  labs(title = "Via Experiementer") +
  scale_fill_manual(values = c("green", "grey", "blue", "red","purple", "orange", "black"))
```

Plotting by Genotype Most Recent Experiment Day (6/29/2023)
```{R}
subset(merged_data, Date== "2023-06-29, 2023-09-06, 2023-06-26")%>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in with UDP candidate sqv-7") +
  scale_fill_manual(values = c("green", "grey", "blue", "red", "purple", "orange", "black")) +
  scale_color_manual(values = c("green", "grey", "blue", "red", "purple", "orange", "black"))
  
```

Plotting by Experimenter Most Recent Experiment (11/10/2023)
```{R}
subset(merged_data, Date== "2023-11-13")%>%
  ggplot(aes(x = Genotype , y = Response.time)) +
  stat_summary(geom= "bar", fun= "mean", aes(fill = Genotype), width= 0.5) +
  scale_y_continuous(expand = c(0,0)) +
  geom_text(aes(x=1, y=12, label="Stretch it"), vjust=-1) +
  labs(title = "4mM OA SOS with 30pct Octanol 40min") +
  scale_fill_manual(values = c("grey", "blue"))
  
```

Plotting by N2, TBH, CEST-2.1, GLO-1
```{R}
subset(merged_data, Date== "2023-06-19,2023-06-22,2023-06-23,2023-06-26,2023-06-29")%>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  geom_boxplot(aes(fill = Genotype)) +
  labs(title = "30% Octanol avoidance on OA pathayway") +
  scale_fill_manual(values = c("green", "grey", "blue", "red","purple", "orange", "black")) +
  scale_color_manual(values = c("green", "grey", "blue", "red", "purple", "orange", "black"))
  
```
Plotting by N2, sqv7-, CEST-2.1 

```{R}
 data<-data.frame(subset(merged_data, Date %in% c("2023-06-29", "2023-09-06", "2023-06-26"))) 

 ####### anova ####
 lm(data = data, formula = Response.time ~ Genotype) %>%
  summary()

  ggplot(data, aes(x=Genotype, y= Response.time)) +
  stat_summary(geom= "bar", fun= "mean", aes(fill = Genotype), width= 0.5) + 
    scale_x_discrete(limits = c("N2","cest-2.1", "sqv-7")) +
    
     scale_y_continuous(expand = c(0,0)) +
  geom_text(aes(x=1, y=12, label="Stretch it"), vjust=-1) +
    
    scale_fill_manual(values = c("green", "grey", "blue")) +
     stat_summary(geom = "errorbar", fun.data = "mean_se", width = .2) +
      theme(legend.text = element_text(face = "italic")) +
  theme(axis.text = element_text(face = "italic")) +
    theme(text = element_text(size=20)) +
    labs(y= "Time(sec)")
  
 
```
Plotting by N2, TBH, CEST-2.1 
```{R}
 data<-data.frame(subset(merged_data, Date== "2023-06-26,2023-06-29,2023-06-23,2023-05-24")) 

 ####### anova ####
 lm(data = data, formula = Response.time ~ Genotype) %>%
  summary()

  ggplot(data, aes(x=Genotype, y= Response.time, width = 0.75)) +
  geom_bar(stat="summary", aes(fill = Genotype)) + 
    scale_x_discrete(limits = c('N2', 'ugt-64 ', 'sqv-7')) +
    
     scale_y_continuous(expand = c(0,0)) +
  geom_text(aes(x=1, y=12, label="Stretch it"), vjust=-1) +
    
    scale_fill_manual(values = c("green", "grey", "blue")) +
  scale_color_manual(values = c("green", "grey", "blue")) +
     stat_summary(geom = "errorbar", fun.data = "mean_se", width = .2) +
 
     labs(title = "30% octanol avoidance with N2, cest-2.1, and tbh-1")
```


```{R}
 datas<-data.frame(subset(merged_data, Genotype == 'N2, cest-2.1, tbh-1'))

  ggplot(data, aes(x=Genotype, y= Response.time, width = 0.75)) +
  geom_bar(stat="summary", aes(fill = Genotype)) + 
    
     scale_y_continuous(expand = c(0,0)) +
  geom_text(aes(x=1, y=12, label="Stretch it"), vjust=-1) +
    scale_x_discrete(limits = c("N2","cest-2.1", "tbh-1")) +
    
    scale_fill_manual(values = c("green", "grey", "red")) +
  scale_color_manual(values = c("green", "grey", "red")) +
     stat_summary(geom = "errorbar", fun.data = "mean_se", width = .2) +
    
     theme(legend.text = element_text(face = "italic")) +
  theme(axis.text = element_text(face = "italic")) +
 
     labs(title = "30% octanol avoidance with N2, cest-2.1, and tbh-1")
  
 
```

```{R}
#I made dome changes - the edited code are annotated
library(tidyverse)
data<-filter(merged_data, Genotype %in% c("N2", "cest-2.1", "tbh-1")) 
ggplot(data, aes(x=Genotype, y= Response.time, width = 0.75)) +
  geom_bar(stat="summary", aes(fill = Genotype)) +
  scale_y_continuous(expand = c(0,0)) +
  geom_text(aes(x=1, y=12, label="Stretch it"), vjust=-1) +
  scale_x_discrete(limits = c('N2', 'cest-2.1', 'tbh-1')) +
  scale_fill_manual(values = c("blue", "green", "red")) +
  scale_color_manual(values = c("blue", "green", "red")) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = .2) +
  theme(legend.text = element_text(face = "italic")) +
  theme(axis.text = element_text(face = "italic")) +
  labs(title = "30% octanol avoidance with N2, cest-2.1, and tbh-1")
  
 
```

Plotting by N2, TBH, CEST-2.1 
```{R}
 data<-data.frame(subset(merged_data, Date== "2023-06-26, 2023-06-29, 2023-06-23, 2023-05-24") + Genotype %in% c("N2", "ugt-64", "sqv-7")) 

  ggplot(data, aes(x=Genotype, y= Response.time, width = 0.75)) +
  geom_bar(stat="summary", aes(fill = Genotype)) + 
    scale_x_discrete(limits = c("N2", "ugt-64" , "sqv-7")) +
    
     scale_y_continuous(expand = c(0,0)) +
  geom_text(aes(x=1, y=12, label="Stretch it"), vjust=-1) +
    
    scale_fill_manual(values = c("green", "grey", "blue")) +
  scale_color_manual(values = c("green", "grey", "blue")) +
     stat_summary(geom = "errorbar", fun.data = "mean_se", width = .2) +
 
     labs(title = "cest-2.1 Behavioral 30% Smell on Stick(SOS) Phenotype")
```

mutate(genotype = fct_relevel(genotype, "N2")) 
z stat_summary(geom = "bar", aes(fill = genotype), width = 0.75) +

Let's plot the means:


```{r}
merged_data %>%
  filter(Date != "2021-08-27") %>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  stat_summary(fun.data = "mean_se")
```

Plotting by Date Ranges
```{r}
  data<-data.frame(subset(merged_data, Date== "2023-09-06")) +
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in cest-2.1") +
  scale_fill_manual(values = c("green", "grey", "purple")) +
  scale_color_manual(values = c("green", "grey", "purple"))
```
```{r}
  merged_data%>%
  filter(between(Date, as.Date('2023-06-19'), as.Date ('2023-06-29')))%>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in cest-2.1") +
  scale_fill_manual(values = c("green", "grey", "blue", "red","purple", "orange", "black")) +
  scale_color_manual(values = c("green", "grey", "blue", "red","purple", "orange","black")) +
   facet_grid(~Date)
```


```{r}
  merged_data%>%
  filter(between(Date, as.Date('2023-04-05'), as.Date ('2022-10-13')))%>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in cest-2.1") +
  scale_fill_manual(values = c("green", "grey", "blue", "red","purple", "orange", "black")) +
  scale_color_manual(values = c("green", "grey", "blue", "red","purple", "orange", "black")) +
   facet_grid(~Date)
```
```{r}
  subset(merged_data, Date== "2023-06-19")%>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "Dilute 30% octanol SOS on 2023-02-02") +
  scale_fill_manual(values = c("green", "grey", "blue", "red")) +
  scale_color_manual(values = c("green", "grey", "blue", "red"))
```

Plotting by Date Ranges
```{r}
  merged_data%>%
  filter(between(Date, as.Date('2023-06-19'), as.Date ('2023-06-29')))%>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  scale_x_discrete(limits = c("N2","cest-2.1", "tbh-1", "glo-1", "ugt-64", "sqv-7")) + 
  theme(legend.text = element_text(face = "italic")) +
  theme(axis.text = element_text(face = "italic")) +
  labs(title = "30% oct avoidance in cest-2.1 last 5 experiment days") +
  scale_fill_manual(values = c("green", "grey", "blue", "red","purple", "orange", "black")) +
  scale_color_manual(values = c("green", "grey", "blue", "red","purple", "orange", "black"))
```

Plotting by Date Ranges
```{r}
  merged_data%>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  scale_x_discrete(limits = c("N2","cest-2.1", "tbh-1", "glo-1", "ugt-64","trangenics", "sqv-7")) + 
  theme(legend.text = element_text(face = "italic")) +
  theme(axis.text = element_text(face = "italic")) +
  labs(title = "30% oct avoidance in cest-2.1 last 5 experiment days") +
  scale_fill_manual(values = c("green", "grey", "blue", "red","purple", "orange", "black")) +
  scale_color_manual(values = c("green", "grey", "blue", "red","purple", "orange", "black"))
```

```{R}
#I made dome changes - the edited code are annotated
library(tidyverse) 
merged_data%>%
ggplot(aes(x=Genotype, y= Response.time)) +
  stat_summary(geom= "bar", fun= "mean", aes(fill = Genotype), width= 0.5) +
  scale_y_continuous(expand = c(0,0)) +
  geom_text(aes(x=1, y=12, label="Stretch it"), vjust=-1) +
  scale_x_discrete(limits = c("N2","cest-2.1", "tbh-1", "glo-1", "ugt-64", "sqv-7")) +
  scale_fill_manual(values = c("green", "grey", "blue", "red","purple", "orange")) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2) +
  theme(legend.text = element_text(face = "italic")) +
  theme(axis.text = element_text(face = "italic")) +
  theme(text = element_text(size=20))+
labs(y= "Time(sec)")
```

