---
title: "Cest2.1_OctAvoidance"
author: "Tia"
Date: "04/05/2021"
output: 
  html_document:
    code_folding: hide
---

30pct Octanol Avoidance

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
theme_set(theme_classic())
files <- fs::dir_ls(recurse = TRUE, glob = "data/octanol_3*.csv")
merged_data <- files %>% purrr::map_df(., readr::read_csv, .id = "filename")
library(dplyr)

```

Plotting by Genotype
```{R}
merged_data %>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in cest-2.1") +
  scale_fill_manual(values = c("green", "grey", "blue", "red")) +
  scale_color_manual(values = c("green", "grey", "blue", "red"))
  
```
Plot by Date

```{r}
merged_data %>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in cest-2.1") +
  scale_fill_manual(values = c("green", "grey", "blue", "red")) +
  scale_color_manual(values = c("green", "grey", "blue", "red")) +
  facet_grid(~Date)
```

Plotting by Genotype (excluding 8-27)
```{R}
merged_data %>%
  filter(Date != "2021-08-27") %>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in cest-2.1") +
  scale_fill_manual(values = c("green", "grey", "blue", "red")) +
  scale_color_manual(values = c("green", "grey", "blue", "red"))
  
```

Plotting by Experimenter

```{r}
merged_data %>%
  filter(Date != "2021-08-27") %>%
  ggplot(aes(x = Experimenter, y = Response.time)) +
  geom_boxplot(aes(fill = Genotype)) +
  labs(title = "Via Experiementer") +
  scale_fill_manual(values = c("blue", "grey", "blue", "red"))
```

Plotting by Genotype Most Recent Experiment Day (04/06/2022)
```{R}
subset(merged_data, Date== "2022-10-13")%>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in cest-2.1") +
  scale_fill_manual(values = c("green", "grey", "blue", "red")) +
  scale_color_manual(values = c("green", "grey", "blue", "red"))
  
```

Plotting by Experimenter Most Recent Experiment (12/14/2022)
```{R}
subset(merged_data, Date== "2022-12-14")%>%
  ggplot(aes(x = Experimenter, y = Response.time)) +
  geom_boxplot(aes(fill = Genotype)) +
  labs(title = "Via Experiementer") +
  scale_fill_manual(values = c("blue", "grey", "blue", "red"))
  
```

Plotting by N2, TBH, CEST-2.1 
```{R}
subset(merged_data, Date== "2022-04-05,2022-05-10,2022-04-27")%>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  geom_boxplot(aes(fill = Genotype)) +
  labs(title = "30% Octanol avoidance on OA pathayway") +
  scale_fill_manual(values = c("green", "grey", "blue", "red")) +
  scale_color_manual(values = c("green", "grey", "blue", "red"))
  
```
Plotting by N2, TBH, CEST-2.1 
```{R}
 data<-data.frame(subset(merged_data, Date== "2022-04-05,2022-05-10,2022-04-27")) 

 ####### anova ####
 lm(data = data, formula = Response.time ~ Genotype) %>%
  summary()

  ggplot(data, aes(x=Genotype, y= Response.time, width = 0.75)) +
  geom_bar(stat="summary", aes(fill = Genotype)) + 
    
     scale_y_continuous(expand = c(0,0)) +
  geom_text(aes(x=1, y=12, label="Stretch it"), vjust=-1) +
    
    scale_fill_manual(values = c("green", "grey", "blue")) +
  scale_color_manual(values = c("green", "grey", "blue")) +
     stat_summary(geom = "errorbar", fun.data = "mean_se", width = .2) +
 
     labs(title = "cest-2.1 behavioral 30% SOS Phenotype")
  
 
```

mutate(genotype = fct_relevel(genotype, "N2")) 
z stat_summary(geom = "bar", aes(fill = genotype), width = 0.75) +

Let's plot the means:


```{r}
merged_data %>%
  filter(Date != "2021-08-27") %>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  stat_summary(fun.data = "mean_se")
```


```{r}
  merged_data%>%
  filter(between(Date, as.Date('2021-08-05'), as.Date ('2021-09-07')))%>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in cest-2.1") +
  scale_fill_manual(values = c("green", "grey", "blue", "red")) +
  scale_color_manual(values = c("green", "grey", "blue", "red")) +
   facet_grid(~Date)
```
```{r}
  merged_data%>%
  filter(between(Date, as.Date('2021-09-29'), as.Date ('2022-03-25')))%>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in cest-2.1") +
  scale_fill_manual(values = c("green", "grey", "blue", "red")) +
  scale_color_manual(values = c("green", "grey", "blue", "red")) +
   facet_grid(~Date)
```


```{r}
  merged_data%>%
  filter(between(Date, as.Date('2022-04-05'), as.Date ('2022-10-13')))%>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in cest-2.1") +
  scale_fill_manual(values = c("green", "grey", "blue", "red")) +
  scale_color_manual(values = c("green", "grey", "blue", "red")) +
   facet_grid(~Date)
```
```{r}
  subset(merged_data, Date== "2023-02-02")%>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "Dilute 30% octanol SOS on 2023-02-02") +
  scale_fill_manual(values = c("green", "grey", "blue", "red")) +
  scale_color_manual(values = c("green", "grey", "blue", "red"))
```







