---
title: "Cest2.1_OctAvoidance"
author: "TB"
Date: "2021-2024"
output: 
  html_document:
    code_folding: hide
---

30pct Octanol Avoidance

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
library(ggtext)
theme_set(theme_classic())
files <- fs::dir_ls(recurse = TRUE, glob = "data/octanol_3*.csv")
merged_data <- files %>% purrr::map_df(., readr::read_csv, .id = "filename")
library(dplyr)

```

Plotting All Data by Genotype
```{R}
merged_data %>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in cest-2.1") +
  scale_fill_manual(values = c("green", "grey", "blue", "red", "purple", "orange", "black","white","hotpink1","gold")) +
  scale_color_manual(values = c("green", "grey", "blue", "red", "purple", "orange", "black","white","hotpink1","gold"))
  
```

Plotting by Genotype (excluding 8-27)
```{R}
merged_data %>%
  filter(Date != "2021-08-27") %>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in cest-2.1") +
  scale_fill_manual(values = c("green", "grey", "blue", "red", "purple", "orange", "black","white","hotpink1","gold")) +
  scale_color_manual(values = c("green", "grey", "blue", "red", "purple", "orange", "black","white","hotpink1","gold"))
  
```

Plotting by Genotype Most Recent Experiment Day(s) (3)
```{R}
subset(merged_data, Date== "2023-06-29, 2023-09-06, 2023-06-26")%>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in with UDP candidate sqv-7") +
  scale_fill_manual(values = c("green", "grey", "blue", "red", "purple", "orange", "black")) +
  scale_color_manual(values = c("green", "grey", "blue", "red", "purple", "orange", "black"))
  
```

Plotting by Genotype Most Recent Experiment Day with Bar graph
```{R}
data<-data.frame(subset(merged_data, Date %in% c("2023-11-10")))
  ggplot(aes(x = Genotype , y = Response.time)) +
  stat_summary(geom= "bar", fun= "mean", aes(fill = Genotype), width= 0.5) +
  scale_y_continuous(expand = c(0,0)) +
  geom_text(aes(x=1, y=12, label="Stretch it"), vjust=-1) +
  labs(title = "4mM OA SOS with 30pct Octanol 40min") +
  scale_fill_manual(values = c("green", "grey", "blue")) + 
  scale_color_manual(values = c( "green", "grey", "blue"))
```

  Plotting by Experimenter
```{r}
merged_data %>%
  filter(Date != "2021-08-27") %>%
  ggplot(aes(x = Experimenter, y = Response.time)) +
  geom_boxplot(aes(fill = Genotype)) +
  labs(title = "Via Experiementer") +
  scale_fill_manual(values = c("green", "grey", "blue", "red", "purple", "orange", "black","white","hotpink1","gold"))
```

Plotting by Date
```{r}
merged_data %>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in cest-2.1") +
  scale_fill_manual(values = c("green", "grey", "blue", "red", "purple", "orange", "black","white","hotpink1","gold")) +
  scale_color_manual(values = c("green", "grey", "blue", "red", "purple", "orange", "black","white","hotpink1","gold")) +
  facet_grid(~Genotype)
```

Specific Time period
```{r}
  merged_data%>%
  filter(between(Date, as.Date('2023-06-19'), as.Date ('2023-06-29')))%>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "30% oct avoidance in cest-2.1") +
  scale_fill_manual(values = c("green", "grey", "blue", "red","purple", "orange", "black")) +
  scale_color_manual(values = c("green", "grey", "blue", "red","purple", "orange","black")) +
   facet_grid(~Date)
```

Specific Assay

Plotting by N2, TBH, CEST-2.1, GLO-1
```{R}
subset(merged_data, Date== "2023-06-19,2023-06-22,2023-06-23,2023-06-26,2023-06-29")%>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  geom_boxplot(aes(fill = Genotype)) +
  labs(title = "30% Octanol avoidance on OA pathayway") +
  scale_fill_manual(values = c("green", "grey", "blue", "red","purple", "orange", "black")) +
  scale_color_manual(values = c("green", "grey", "blue", "red", "purple", "orange", "black"))
  
```
Plotting by N2, sqv7-, CEST-2.1 

```{R}
 data<-data.frame(subset(merged_data, Date %in% c("2023-06-29", "2023-09-06", "2023-06-26"))) 

 ####### anova ####
 lm(data = data, formula = Response.time ~ Genotype) %>%
  summary()

  ggplot(data, aes(x=Genotype, y= Response.time)) +
  stat_summary(geom= "bar", fun= "mean", aes(fill = Genotype), width= 0.5) + 
    scale_x_discrete(limits = c("N2","cest-2.1", "sqv-7")) +
    
     scale_y_continuous(expand = c(0,0)) +
  geom_text(aes(x=1, y=12, label="Stretch it"), vjust=-1) +
    
    scale_fill_manual(values = c("green", "grey", "blue")) +
     stat_summary(geom = "errorbar", fun.data = "mean_se", width = .2) +
      theme(legend.text = element_text(face = "italic")) +
  theme(axis.text = element_text(face = "italic")) +
    theme(text = element_text(size=20)) +
    labs(y= "Time(sec)")
  
 
```

Plotting by N2, TBH, CEST-2.1 
```{R}
 data<-data.frame(subset(merged_data, Date== "2023-06-26,2023-06-29,2023-06-23,2023-05-24")) 

 ####### anova ####
 lm(data = data, formula = Response.time ~ Genotype) %>%
  summary()

  ggplot(data, aes(x=Genotype, y= Response.time, width = 0.75)) +
  geom_bar(stat="summary", aes(fill = Genotype)) + 
    scale_x_discrete(limits = c('N2', 'ugt-64 ', 'sqv-7')) +
    
     scale_y_continuous(expand = c(0,0)) +
  geom_text(aes(x=1, y=12, label="Stretch it"), vjust=-1) +
    
    scale_fill_manual(values = c("green", "grey", "blue")) +
  scale_color_manual(values = c("green", "grey", "blue")) +
     stat_summary(geom = "errorbar", fun.data = "mean_se", width = .2) +
 
     labs(title = "30% octanol avoidance with N2, cest-2.1, and tbh-1")
```

Plotting via days with all 3 N2, cest-2.1, and glo-1
```{R}
 #data<-data.frame(subset(merged_data, Genotype == 'N2, cest-2.1, tbh-1'))

data<-data.frame(subset(merged_data, Date== "2023-05-24, 2023-05-08, 2023-05-09, 2023-06-23, 2023-06-19")) 

 data<-filter(data, Genotype %in% c("N2", "cest-2.1", "glo-1")) 

  ggplot(data, aes(x=Genotype, y= Response.time, width= 0.5)) +
  geom_bar(stat="summary", aes(fill = Genotype)) +
    geom_point(aes(color = Genotype)) +
    

     scale_y_continuous(expand = c(0,0)) +
  geom_text(aes(x=1, y=20, label="Stretch it"), vjust=-1) +
    scale_x_discrete(limits = c("N2","cest-2.1", "glo-1")) +
    
    scale_fill_manual(values = c("green", "grey", "red")) +
  scale_color_manual(values = c("green", "grey", "red")) +

     stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2) +
  theme(legend.text = element_text(face = "italic")) +
  theme(axis.text = element_text(face = "italic")) +
  theme(text = element_text(size=12))+
     labs(title = "30% octanol avoidance with all N2, cest-2.1, and glo-1")
  
 
```

Plotting via days with all 3 N2, cest-2.1, and tbh-1-1
```{R}
 #data<-data.frame(subset(merged_data, Genotype == 'N2, cest-2.1, tbh-1'))

library(ggplot2)
library(dplyr)

filter_date <- c("2022-04-05", "2022-04-27", "2022-05-10", "2022-12-14", "2023-02-08", "2023-05-08", "2023-05-10", "2023-06-22", "2023-06-26")

# Filter Data to Date
filtered_data <- merged_data %>%
  filter(Date %in% filter_date, Genotype %in% c("N2", "cest-2.1", "tbh-1"))

# Reorder Genotype 
filtered_data$Genotype <- factor(filtered_data$Genotype, levels = c("N2", "cest-2.1", "tbh-1"))

ggplot(filtered_data, aes(x = Genotype, y = Response.time)) +
    stat_summary(geom = "bar", aes(fill = Genotype), width = 0.5) +
  geom_point(aes(fill = Genotype), color = "black", size = 1, alpha = 0.5, position = position_jitter(width = 0.2)) +
    stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2) +
  #labs(title = "OA SOS with N2, cest-2.1, and tbh-1 for 30% octanol avoidance") +
  scale_y_continuous(expand = c(0, 0)) +
  geom_text(aes(x = 1, y = 20, label = "Stretch it"), vjust = -1) +
  scale_fill_manual(values = c("#999999", "#E69F00", "#D55E00"), name = "Genotype") +
  scale_color_manual(values = c("#999999", "#E69F00", "#D55E00"), name = "Genotype") +
 theme(legend.text = element_text(face = "italic")) +
  theme(axis.text = element_text(face = "italic")) +
  theme(text = element_text(size = 10)) +
  labs(y = "Time(sec)")

  
 
```

Plotting OA Receptors Mutants SOS
With points
```{r}
  subset(merged_data, Date== "2024-04-21")%>%
  ggplot(aes(x = Genotype, y = Response.time)) +
  geom_boxplot() +
  geom_point(aes(color = Genotype)) +
  labs(title = "Dilute 30% octanol SOS on 2024-04-21") +
  scale_fill_manual(values = c("green", "grey", "blue", "red","gold")) +
  scale_color_manual(values = c("green", "grey", "blue", "red","gold"))
```
Into bar grap
```{r}
library(tidyverse)

# Assuming merged_data is your dataframe
filtered_data <- merged_data %>%
  filter(Date %in% c("2024-04-30")) 

ggplot(filtered_data, aes(x=Genotype, y=Response.time)) +
  geom_point(aes(color = Genotype)) +
  stat_summary(geom= "bar", fun= "mean", aes(fill = Genotype), width= 0.5) +
  scale_y_continuous(expand = c(0,0)) +
  geom_text(aes(x=1, y=20, label="Stretch it"), vjust=-1) +
  scale_x_discrete(limits = c("N2","cest-2.1", "ges-1p")) +
  scale_fill_manual(values = c("green", "grey", "blue", "red","purple", "orange")) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2) +
  theme(legend.text = element_text(face = "italic")) +
  theme(axis.text = element_text(face = "italic")) +
  theme(text = element_text(size=10))+
  labs(y= "Time(sec)")

```

Specific Type of Graph
Plotting by adding indivual worms to figure
```{R}
#I made dome changes - the edited code are annotated
library(tidyverse)
data<-filter(merged_data, Genotype %in% c("N2", "cest-2.1", "tbh-1")) 
ggplot(data, aes(x=Genotype, y= Response.time, width = 0.75)) +
  geom_bar(stat="summary", aes(fill = Genotype)) +
  #scale_y_continuous(expand = c(0,0)) +
  ggbeeswarm::geom_quasirandom() +
  geom_jitter() +
  scale_y_log10() +
  geom_text(aes(x=1, y=12, label="Stretch it"), vjust=-1) +
  scale_x_discrete(limits = c('N2', 'cest-2.1', 'tbh-1')) +
  scale_fill_manual(values = c("blue", "green", "red")) +
  scale_color_manual(values = c("blue", "green", "red")) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = .2) +
  theme(legend.text = element_text(face = "italic")) +
  theme(axis.text = element_text(face = "italic")) +
  labs(title = "30% octanol avoidance with N2, cest-2.1, and tbh-1")
  
 
```

Plotting with Jitter Point Function
```{R}
library(tidyverse)
data<-filter(merged_data, Genotype %in% c("N2", "cest-2.1", "tbh-1")) 
ggplot(data, aes(x=Genotype, y= Response.time, width = 0.75)) +
  geom_bar(stat="summary", aes(fill = Genotype)) +
  #scale_y_continuous(expand = c(0,0)) +
  ggbeeswarm::geom_quasirandom() +
  geom_jitter() +
  scale_y_log10() +
  geom_text(aes(x=1, y=12, label="Stretch it"), vjust=-1) +
  scale_x_discrete(limits = c('N2', 'cest-2.1', 'tbh-1')) +
  scale_fill_manual(values = c("blue", "green", "red")) +
  scale_color_manual(values = c("blue", "green", "red")) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = .2) +
  theme(legend.text = element_text(face = "italic")) +
  theme(axis.text = element_text(face = "italic")) +
  labs(title = "30% octanol avoidance with N2, cest-2.1, and tbh-1")
```


```{r}
library(tidyverse)

# The palette with grey:
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# Filter Data to Date
filtered_data <- merged_data %>%
  filter(Date %in% c("2024-04-30", "2024-05-07", "2024-05-10"))

# Define the desired order for the Genotype levels
filtered_data$Genotype <- factor(filtered_data$Genotype, levels = c("N2", "cest-2.1", "MOY00022", "MOY00023"))

ggplot(filtered_data, aes(x = Genotype, y = Response.time)) +
    stat_summary(geom = "bar", aes(fill = Genotype), width = 0.5) +
  geom_point(aes(fill = Genotype), color = "black", size = 1, alpha = 0.5, position = position_jitter(width = 0.2)) +
    stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2) +
  scale_y_continuous(expand = c(0, 0)) +
  geom_text(aes(x = 1, y = 20, label = "Stretch it"), vjust = -1) +
  scale_fill_manual(values = c( "#999999", "#E69F00", "#56B4E9", "#0072B2")) + 
  theme(legend.text = element_text(face = "italic")) +
  theme(axis.text = element_text(face = "italic")) +
  theme(text = element_text(size = 10)) +
  labs(y = "Time(sec)")



```
